Group Meeting

### 2024-02-05 presentations/grp.qmd
update websites
update

---
title: Presentation
format:
  html: default
  revealjs:
    output-file: 'grp-revealjs.html'
---

@@

>>>>

---
title: Group Meeting
format:
  dashboard:
    nav-buttons: [github]
navbar: false
---

# #1 Overview {orientation="columns"}

## Orbits

::: {.card title="Orbit in Heliographic Coordinates"}
![](../images/paste-15.png)
:::

## ENLIL simulation

::: {.card title="ENLIL simulation"}
### Normalized solar wind density at the ecliptic and the IMF lines

![](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4){width="80%"}

### Radial solar wind velocity at the ecliptic on the global and detail regions together with the temporal profile at spacecraft

![](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4){width="80%"}
:::

# #2 Observation

##  {.tabset}

::: {.column-page layout-nrow="1"}
![PSP Observation Overvall](../images/paste-19.png)

![PSP observation](../images/paste-18.png){width="50%"}
:::

::: {.column-page layout-nrow="1"}
![PSP observation](../images/paste-18.png)

![ACE observation](../images/paste-16.png)

![ACE observation (continued)](../images/paste-17.png)
:::

# #3 Plasma Adiabatic Evolution {orientation="columns"}

##  {width="50%"}

###  {.tabset}

@@

##  {.tabset}

::: card
### @perroneRadialEvolutionSolar2019

The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by

$$n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}$$

$$B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT$$

The faster decrease of the magnetic than kinetic pressure is reﬂected in the radial proton plasma beta variation

$$β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}.$$
:::

![](../images/sty3348fig5.jpeg){width="50%"}

# #4 Examples of Discontinuities

![](images/paste-1.png)

![](images/paste-2.png)

![](images/paste-3.png)
